CAT-DWAM, A Question Answering System

### 2011-05-07 paper/paper.tex
edited paper.tex

>>>>

We did pre-process some of the data by running the chunker (which creates
candidate phrases along with part of speech tags) and creating files in
groups of ten questions each with all of the candidates. Running the chunker
took about two minutes per question, so by doing this we were able to have
the whole set of potential candidates instantly ready to go.
